---
title: "cross_validation"
author: "Ashley Tseng"
date: "11/12/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Cross Validation “by hand”
```{r}
nonlin_df = 
  tibble(
    id = 1:100,
    x = runif(100, 0, 1),
    y = 1 - 10 * (x - .3) ^ 2 + rnorm(100, 0, .3)
  )

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + theme_bw()
```

Training and testing
```{r}
train_df = sample_frac(nonlin_df, size = .8)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) + 
  geom_point() + 
  geom_point(data = test_df, color = "red")
```

Fit three models of varying goodness
```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```


### Let's look at some fits

Linear Model:
```{r}
linear_plot = train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

linear_plot
```
Just eyeballing this, this is not a good fit. The line we get from the linear prediction model does not fit the data well.

Smooth Model:
```{r}
smooth_plot = train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

smooth_plot
```
This is a good fit.

Wiggly Model:
```{r}
wiggly_plot = train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point() + 
  geom_line(aes(y = pred), color = "red")

wiggly_plot
```
This is worse than the smooth model but not the worst in the world. It's better than the linear model.

Test dataset:
```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```

Train dataset:
```{r}
rmse(linear_mod, train_df)
rmse(smooth_mod, train_df)
rmse(wiggly_mod, train_df)
```

**You will always pick the model that fits the test dataset better. The training dataset you normally put too much stuff in; it may look lke it's looking better than the test dataset, but in reality it's not. Similar to how adding more covariates to your model increases R^2 always.**

When would wiggly models come in handy? E.g., if I have 40 different environmental pollutants and don't know which one is the worst, I would use cross validation and run different models (linear, smooth, wiggly). 


## Now we will do CV using modelr
```{r}
cv_df = 
  crossv_mc(nonlin_df, 100) 
```

One note about resample...
The way that CV works behind the scenes: Doesn't save all the train and test datasets to be less memory-intensive.
```{r}
cv_df %>% 
  pull(train) %>% 
  .[[1]] %>% 
  as_tibble

cv_df %>% 
  pull(test) %>% 
  .[[1]] %>% 
  as_tibble

cv_df =
  cv_df %>% 
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble))
```


Try fitting the linear model to all of these:
```{r}
cv_df = 
  cv_df %>% 
  mutate(linear_mods  = map(.x = train, ~lm(y ~ x, data = .x)),
         smooth_mods  = map(.x = train, ~mgcv::gam(y ~ s(x), data = .x)),
         wiggly_mods  = map(.x = train, ~gam(y ~ s(x, k = 30), sp = 10e-6, data = .x))) %>% 
  mutate(rmse_linear = map2_dbl(.x = linear_mods, .y = test, ~rmse(model = .x, data = .y)),
         rmse_smooth = map2_dbl(.x = smooth_mods, .y = test, ~rmse(model = .x, data = .y)),
         rmse_wiggly = map2_dbl(.x = wiggly_mods, .y = test, ~rmse(model = .x, data = .y)))
```
To get RMSE, you need to map over 2 columns (hence use map2).


Plot the distribution of RMSE values for each candidate model:
```{r}
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```



## Example: Child Growth
```{r}
child_growth = read_csv("./data/nepalese_children.csv")

child_growth %>% 
  ggplot(aes(x = weight, y = armc)) + 
  geom_point(alpha = .5)
```
Based on visually inspecting the plot, there is maaaybe not a straight line. If we tried to draw a line through the points, we would probbaly curve it.
