---
title: "linear_models"
author: "Ashley Tseng"
date: "11/7/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```

## Model Fitting
```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    boro = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(boro != "Staten Island") %>% 
  select(price, stars, boro, neighborhood, room_type)
```


Fit first linear model!
```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)

summary(fit)
```
 

Tidy the results
```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```



## Take a look at factors
Changing reference group:
```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(
    boro = fct_infreq(boro, ordered = NA),
    room_type = fct_infreq(room_type))
```

Refit the last model
```{r}
fit = lm(price ~ stars + boro, data = nyc_airbnb)
```

Tidy
```{r}
fit %>% 
  broom::tidy() %>% 
  mutate(term = str_replace(term, "boro", "Boro: ")) %>% 
  knitr::kable(digits = 3)
```



## Diagnostics

Looking at what's going on with residuals
```{r}
residuals_violin = 
  modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = boro, y = resid)) +
  geom_violin() +
  ylim(-500, 500)

residuals_violin


residuals_scatter = 
  modelr::add_residuals(nyc_airbnb, fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point() +
  ylim(-500, 500)

residuals_scatter
```


add_predictions is just plugging the values into the regression equation and spitting out the value. add_predictions is the same structure as add_residuals:
```{r}
modelr::add_predictions(nyc_airbnb, fit)
```



## Skipping Hypothesis Testing



## Nesting Data
```{r}
fit_interaction = lm(price ~ stars * boro, data = nyc_airbnb)

fit_interaction %>% 
  broom::tidy()
```
In the Bronx and in Queens, it almost doesn't matter what the number of stars the airbnb has is. In Manhattan, it will depend a lot on the number of stars.


```{r}
fit_interaction = lm(price ~ stars * boro + room_type * boro, data = nyc_airbnb)

fit_interaction %>% 
  broom::tidy()
```
In Manhattan, a shared room is going to cost you on average $154 less.


```{r}
nyc_airbnb %>% 
  lm(price ~ stars * boro + room_type * boro, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


Let's try to map this instead.
```{r}
nest_lm_res =
  nyc_airbnb %>% 
  nest(data = -boro) %>% 
  mutate(models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest(models)
```
Going from an entire home to a shared room in Manhattan will cost you $154 less and $106 less in Brooklyn.



Let's nest neighborhoods:
```{r}
manhattan_nest_lm_res =
  nyc_airbnb %>% 
  filter(boro == "Manhattan") %>% 
  nest(data = -neighborhood) %>% 
  mutate(models = map(.x = data, ~lm(price ~ stars + room_type, data = .x)),
         models = map(models, broom::tidy)) %>% 
  select(-data) %>% 
  unnest(models)

MH_nest_plot = manhattan_nest_lm_res %>% 
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) + 
  geom_point() + 
  facet_wrap(~term) + 
  theme(axis.text.x = element_text(angle = 80, hjust = 1))

MH_nest_plot
```
Private rooms are on the left, shared rooms are on the right. In Battery Park city, private rooms are less expensive than an entire home (~$100 less). In NoHo, it's $200 less to stay in a private room than an entire home.

```{r}
nyc_airbnb %>% 
  filter(neighborhood == "Murray Hill", room_type == "Shared room")
```
Great for exploratory analysis, but not a formal analysis

